### 2023-08-15 README.Rmd
add github actions to build README.md on push

This repository contains the data and code for our paper:
<!--
> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:
-->
> Bartholdy, B.P., Hasselstrøm, J.B., Sørensen, L.K., Casna, M., Hoogland, M., Historisch Genootschap Beemster, & Henry, A.G. (2023). _`r Title`_. Zenodo, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.7649151>

@@

Use the above paper to cite this compendium.
<!--
Please cite this compendium as:

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and knit to produce the PDF manuscript (`_output/`),
  or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console.

>>>>

This repository contains the data and code for our paper:

<!--
> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:
-->

> Bartholdy, B.P., Hasselstrøm, J.B., Sørensen, L.K., Casna, M., Hoogland, M., Historisch Genootschap Beemster, & Henry, A.G. (2023). _`r Title`_. Zenodo, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.7649151>

@@

Use the above paper to cite this compendium.

<!--
Please cite this compendium as:

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and **render** to produce the PDF manuscript (`_output/`),
  or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console.
